PineAPPL: combining EW and QCD corrections\\ for fast evaluation of LHC processes

### 2020-10-26 paper/sec-results.tex
Add more adjustments for issue 7

The process receives its leading contribution from $\mathrm{qg}$- and
$\bar{\mathrm{q}}\mathrm{g}$-initiated channels, which account for about \SI{65}{\percent}
of the cross section, with some variations in the relative contributions from
individual quark and antiquark flavours as the transverse momentum of the
Z boson varies; the PI contribution always remain negligible.
Overall, the EW corrections suppress the theoretical predictions by about
\SIrange{2}{10}{\percent} as the transverse momentum of the Z boson increases.
The size of this shift is as large as the data uncertainty up to
$p_{\mathrm{T}}^{\ell\bar\ell}\sim \SI{200}{\giga\electronvolt}$, and 
exceeds it by about \SI{60}{\percent} at larger values of
$p_\mathrm{T}^{\ell \bar{\ell}}$. As a consequence,
we anticipate the inclusion of EW corrections to be relevant for an accurate
fit of this data.

The size of the EW correction is between four and twenty times larger than the
size of the PDF uncertainty: as previously noted in the other cases, this fact
suggests that, once included in a PDF fit, EW corrections can improve the
accuracy of the PDFs. In comparison to the scale uncertainty, the size of the
EW corrections remains negligible at small values of $p_{\mathrm{T}}^{\ell\bar\ell}$,
roughly $p_{\mathrm{T}}^{\ell\bar\ell}\lesssim\SI{400}{\giga\electronvolt}$, while it
becomes up to four times larger than it in the two bins at the largest value of
$p_{\mathrm{T}}^{\ell\bar\ell}$. In this kinematic region, NLO EW corrections might
therefore become even more relevant than NNLO QCD corrections, and should
therefore be mandatorily included in a fit of PDFs to this data set.
Finally, the Monte Carlo uncertainty is well under control, as it remains
mostly negligible in comparison to the PDF, scale and data uncertainty, and to
the size of the EW correction.

>>>>

The process receives its leading contribution from $\mathrm{qg}$- and
$\bar{\mathrm{q}}\mathrm{g}$-initiated channels, which account for about \SI{79}{\percent}
of the cross section, with some variations in the relative contributions from
individual quark and antiquark flavours as the transverse momentum of the
Z boson varies; the PI contribution always remain negligible.
Overall, the EW corrections suppress the theoretical predictions by about
\SIrange{2}{15}{\percent} as the transverse momentum of the Z boson increases.
The size of this shift is as large (or slightly larger) as the data uncertainty over
the entire range of $p_{\mathrm{T}}^{\ell\bar\ell}$. As a consequence,
we anticipate the inclusion of EW corrections to be relevant for an accurate
fit of this data.

The size of the EW correction is between four and fifteen times larger than the
size of the PDF uncertainty: as previously noted in the other cases, this fact
suggests that, once included in a PDF fit, EW corrections can improve the
accuracy of the PDFs. In comparison to the scale uncertainty, the size of the
EW corrections remains negligible at small values of $p_{\mathrm{T}}^{\ell\bar\ell}$,
roughly $p_{\mathrm{T}}^{\ell\bar\ell}\lesssim\SI{400}{\giga\electronvolt}$, while it
becomes larger than it in the two bins at the largest value of
$p_{\mathrm{T}}^{\ell\bar\ell}$. In this kinematic region, NLO EW corrections might
therefore become even more relevant than NNLO QCD corrections, and should
therefore be mandatorily included in a fit of PDFs to this data set.
Finally, the Monte Carlo uncertainty is well under control, as it remains
mostly negligible in comparison to the PDF, scale and data uncertainty, and to
the size of the EW correction.
